Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-19 writeup/gz_hubble_data.tex
GEMS/GZH comparison, part 2

Clumpy galaxies in GZH have $n$ and $R_e$ \galfit{} parameters more consistent with disky, $n<2.5$ galaxies than spheroids (Figure~\ref{fig:clumpy_gems}).

\begin{figure}
\begin{center}
\includegraphics[width=0.50\textwidth]{figures/gems_clumpy.png}
\caption{Parameter distributions for GEMS galaxies in \citet{hau07} and GZH. Red and blue points indicate galaxies split by their \sersic~index into disk- and bulge-dominated galaxies. Galaxies identified as ``clumpy'' in GZH are labeled in green.}
\label{fig:clumpy_gems}
\end{center}
\end{figure}

>>>>

We visually inspect galaxies for which the \galfit{} and GZH measurements indicate strong disagreement. Of the 84~galaxies with $n>2.5$ and \pbest$\ge0.80$, almost all are spirals with obvious disks and clearly marked spiral arms. These appear to be cases where \galfit{} fits the bulge at the center, but misses extended emission from the disk. We also examine the 35~galaxies with $n<2.5$ and \pbest$\le0.20$; these galaxies generally have smoother light profiles with no spiral arms, although several have bars and/or the sharper truncation of light near the edges that indicates an S0 galaxy. These galaxies are also significantly bluer $(\langle m_{606}-m_{850}\rangle=0.27\pm3.3)$ compared to the majority of galaxies classified as ``smooth'' in GZH $(\langle m_{606}-m_{850}\rangle=1.2\pm1.7)$. We interpret this as evidence for the fact that single-component radial fits are often inadequate to accurately characterize galaxy morphology, and that a simple cut risks significant amounts of misclassified objects.

Clumpy galaxies in GZH have \galfit{} parameters more consistent with disky, $n<2.5$ galaxies than spheroids (Figure~\ref{fig:clumpy_gems}). Using the thresholds in Table~\ref{tbl:thresholds}, GZH clumpy galaxies have average values of $n=1.6\pm1.2$ and $R_e=32\pm16$~pix, with only 11\% of clumpy galaxies falling in the bulge-dominated region of $n>2.5$.

\begin{figure}
\begin{center}
\includegraphics[width=0.50\textwidth]{figures/gems_clumpy.png}
\caption{Parameter distributions for GEMS galaxies in \citet{hau07} and GZH. Red and blue points indicate galaxies split by their \sersic~index (at $n=2.5$) into disk- and bulge-dominated galaxies, respectively. Galaxies identified as ``clumpy'' in GZH are labeled in green.}
\label{fig:clumpy_gems}
\end{center}
\end{figure}
